Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area" \\ [1ex] \large Supplementary Information

### 2021-08-30 paper/main.tex
citation of datasets v1

\todo[inline]{\textbf{My notes:}\par
    1. change url(s) of datasets\par
    2. cross-referencing to Supplementary Figures does not work but show
``??''. Referencing from suppl.tex to main.tex works tough
}

@@

\todo[inline]{The dataset (\citep{haeusler2021ppa}) should probably be cited here + datalad yada yada}

@@

% intro
Third, we inspected results from both naturalistic paradigms on the level of
individual participants, and compared them to the individual PPA localizations
provided by \citet{sengupta2016extension}, who reported
% Sengupta et al., 2016; unilateral in sub-04 and sub-20
bilateral parahippocampal clusters in 12 of 14 participants and unilateral right
clusters in two participants \citep[see Table~3 in][]{sengupta2016extension}.
% one contrast to localize them all; "...and $Z$>3.4 for all"
Unlike \citet{sengupta2016extension}, who determined PPA clusters using three
candidate contrasts and a variable threshold, we used a single contrast for each
naturalistic stimulus and a uniform threshold for all participants.
% ref to figure
Figure~\ref{fig:subs-thresh-ppa} depicts thresholded $Z$-maps of the primary
movie and audio-description $t$-contrasts, in comparison to the results of a
conventional block-design localizer (see Figure~\ref{fig:subjs_ao_av_c1_surf}
for surface plot; sunthresholded $Z$-maps are provided at
NeuroVault).
% AV
Results of the primary movie contrast yielded bilateral clusters in five
participants, a unilateral right cluster in six participants (of which one
participant yielded a unilateral cluster in the visual localizer), and a
unilateral left cluster in one participant.
% difference to dedicated localizer
We find bilateral clusters for participant \texttt{sub-20}, whereas the
block-design localizer yielded only one cluster in the right hemisphere.
% report here in group
Results of the primary audio-description contrast yielded bilateral clusters in
nine participants that are within or overlapping with the block-design localizer
results.
% subj-04
In participant \texttt{sub-04}, two bilateral clusters are apparent, whereas
block-design localizer, and movie stimulus yielded only one cluster in the right
hemisphere.
% sub-09
For another participant (\texttt{sub-09}) the analysis yielded one cluster in
the left-hemispheric PPA.

@@

% data sources
% https://github.com/psychoinformatics-de/studyforrest-data-aligned/tree/master/code
% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}
The current analyses were carried out on the same preprocessed fMRI data that were used
for the technical validation analysis presented in \citet{hanke2016simultaneous}, and available from \href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{github.com/ psychoinformatics-de/studyforrest-data-aligned}.
Of those 15 participants in the studyforrest dataset that took
part in all three experiments,
% exclusion of VP 10
data of one participant were dropped due to invalid distortion correction
during scanning of the audio-description stimulus.
Data were corrected for motion, aligned with and re-sliced onto a
participant-specific BOLD template image \citep{sengupta2016extension}
(uniform spatial resolution of \unit[2.5$\times$2.5$\times$2.5]{mm} for both
audio-description and movie data).
% preprocessing intro
Preprocessing was performed by FEAT v6.00 (FMRI Expert Analysis Tool \citep{woolrich2001autocorr}) as shipped with
FSL v5.0.9 (\href{https://www.fmrib.ox.ac.uk/fsl}{FMRIB's Software Library}
 \citep{smith2004fsl}) on a computer-cluster running
\href{http://neuro.debian.net}{NeuroDebian} \citep{halchenko2012open}.

@@

% Zenodo (registered but zipped) vs. OSF (datalad dataset but probably
% unregistered)
The fMRI data, annotations, and results are available as Datalad \citep{datalad} datasets,
published to or linked from the
GIN repository \href{https://gin.g-node.org/chaeusler/studyforrest-ppa-analysis}{\url{gin.g-node.org/chaeusler/studyforrest-ppa-analysis}} (DOI assignment pending).
The fMRI datasets for the movie and the audio-description were used in their original form, as published and available on the legacy OpenFMRI portal (\url{https://legacy.openfmri.org/dataset/ds000113}, \url{https://legacy.openfmri.org/dataset/ds000113c}, \url{https://legacy.openfmri.org/dataset/ds000113d}), as well as from \url{https://www.studyforrest.org} in the form of DataLad datasets.
The same data are available in a modified and merged form on OpenNeuro at \url{https://openneuro.org/datasets/ds000113}.
Unthresholded $Z$-maps of all contrasts can be found at
\href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZ}}.

>>>>

@@

@@

% intro
Third, we inspected results from both naturalistic paradigms on the level of
individual participants, and compared them to the individual PPA localizations
provided by \citet{sengupta2016extension}, who reported
% Sengupta et al., 2016; unilateral in sub-04 and sub-20
bilateral parahippocampal clusters in 12 of 14 participants and unilateral right
clusters in two participants \citep[see Table~3 in][]{sengupta2016extension}.
% one contrast to localize them all; "...and $Z$>3.4 for all"
Unlike \citet{sengupta2016extension}, who determined PPA clusters using three
candidate contrasts and a variable threshold, we used a single contrast for each
naturalistic stimulus and a uniform threshold for all participants.
% ref to figure
Figure~\ref{fig:subs-thresh-ppa} depicts thresholded $Z$-maps of the primary
movie and audio-description $t$-contrasts, in comparison to the results of a
conventional block-design localizer (see Figure~\ref{fig:subjs_ao_av_c1_surf}
for surface plot; unthresholded $Z$-maps are provided at
\href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZ}}).
% AV
Results of the primary movie contrast yielded bilateral clusters in five
participants, a unilateral right cluster in six participants (of which one
participant yielded a unilateral cluster in the visual localizer), and a
unilateral left cluster in one participant.
% difference to dedicated localizer
We find bilateral clusters for participant \texttt{sub-20}, whereas the
block-design localizer yielded only one cluster in the right hemisphere.
% report here in group
Results of the primary audio-description contrast yielded bilateral clusters in
nine participants that are within or overlapping with the block-design localizer
results.
% subj-04
In participant \texttt{sub-04}, two bilateral clusters are apparent, whereas
block-design localizer, and movie stimulus yielded only one cluster in the right
hemisphere.
% sub-09
For another participant (\texttt{sub-09}) the analysis yielded one cluster in
the left-hemispheric PPA.

@@

% data sources
The current analyses were carried out on the same preprocessed fMRI data
\citep{hanke2016aligned} that were used for the technical validation analysis
presented in \citet{hanke2016simultaneous}.
% exclusion of VP 10
Of those 15 participants in the studyforrest dataset that took part in all three
experiments, data of one participant were dropped due to invalid distortion
correction during scanning of the audio-description stimulus.
% preprocessing of pre-aligned data
Data were corrected for motion, aligned with and re-sliced onto a
participant-specific BOLD template image \citep{sengupta2016extension} (uniform
spatial resolution of \unit[2.5$\times$2.5$\times$2.5]{mm} for both
audio-description and movie data).
% preprocessing intro
Preprocessing was performed by FEAT v6.00 (FMRI Expert Analysis Tool
\citep{woolrich2001autocorr}) as shipped with FSL v5.0.9
(\href{https://www.fmrib.ox.ac.uk/fsl}{FMRIB's Software Library}
\citep{smith2004fsl}) on a computer-cluster running
\href{http://neuro.debian.net}{NeuroDebian} \citep{halchenko2012open}.

@@

\todo[inline]{Datasets are not cited / do not occur in the references}
\todo[inline]{I did not know how to cite because authors are intersection /
union of the papers, how to order authors\dots}

% new; PPA analysis
All fMRI data, annotations, and results are available as Datalad \citep{datalad}
datasets, published to or linked from the GIN repository
\href{https://gin.g-node.org/chaeusler/studyforrest-ppa-analysis}{\url{gin.g-node.org/chaeusler/studyforrest-ppa-analysis}}
(DOI assignment pending) \citep{haeusler2021ppa}.
% original
Raw data of the audio-description, movie and visual localizer were originally
published on the \emph{OpenfMRI} portal
(\url{https://legacy.openfmri.org/dataset/ds000113}\citep{Hanke2014ds000113},
\url{https://legacy.openfmri.org/dataset/ds000113d}\citep{hanke2016ds000113d}).
% visual localizer
Results from the localization of higher visual areas are available as Datalad
datasets at
\emph{GitHub} (
\href{https://github.com/psychoinformatics-de/studyforrest-data-visualrois}{\url{github.com/psychoinformatics-de/studyforrest-data-visualrois}}\citep{sengupta2016extensiondata}).
% raw data
The realigned participant-specific timeseries that were used in the current analyses were derived from the raw data releases and are available as Datalad
datasets at \emph{GitHub} (
\href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{\url{github.com/psychoinformatics-de/studyforrest-data-aligned}}
\citep{hanke2016aligned}).
% cut annotation
The annotation of cuts is available at \emph{F1000Research} (
\href{https://doi.org/10.5256/f1000research.9536.d134823}{\url{doi.org/10.5256/f1000research.9536.d134823}}
\citep{haeusler2016cutdata}),
% speech annotation
the annotation of speech is available at \emph{OSF}
(\href{https://doi.org/10.17605/OSF.IO/F5J3E}{\url{doi.org/10.17605/OSF.IO/F5J3E}}
\citep{haeusler2020speechdata}).
% surface data
Participant-specific reconstructed cortical surface are available as Datalad
dataset at \emph{GitHub} (
\href{https://gin.g-node.org/studyforrest/cortical-surfaces-freesurfer}{\url{gin.g-node.org/studyforrest/cortical-surfaces-freesurfer}}
\citep{hanke2016freesurferdata}).

\bigbreak
% old
The fMRI data, annotations, and results are available as Datalad \citep{datalad} datasets,
published to or linked from the
GIN repository
\href{https://gin.g-node.org/chaeusler/studyforrest-ppa-analysis}{\url{gin.g-node.org/chaeusler/studyforrest-ppa-analysis}}
(DOI assignment pending) \citep{haeusler2021ppa}.
% AO & AV
The fMRI datasets for the movie and the audio-description were used in their original form, as published and available on the legacy OpenFMRI portal (\url{https://legacy.openfmri.org/dataset/ds000113}, \url{https://legacy.openfmri.org/dataset/ds000113c}, \url{https://legacy.openfmri.org/dataset/ds000113d}), as well as from \url{https://www.studyforrest.org} in the form of DataLad datasets.
The same data are available in a modified and merged form on OpenNeuro at \url{https://openneuro.org/datasets/ds000113}.
Unthresholded $Z$-maps of all contrasts can be found at
\href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZ}}.

### 2021-08-30 paper/suppl.tex
citation of datasets v1

\todo[inline]{I added table of contents & figure. s. Guidelines: ``A table of 
contens should be included on the first page, listing the page number of each 
supplementary figure``}

@@

% individiaul results; intro
Figure~\ref{fig:subjs_ao_av_c1_surf} shows the individual results of
the movie's primary contrast (\texttt{vse\_new > vpe\_old}) and
audio-description's primary contrast (\texttt{geo, groom} > non-spatial noun
categories) mapped onto subject-specific cortical surfaces.
% reconstruction
% \href{https://github.com/psychoinformatics-de/studyforrest-data-freesurfer.git}{dataset}
\href{https://surfer.nmr.mgh.harvard.edu}{FreeSurfer} v5.3.0
\citep{dale1999cortical} was used to reconstruct surfaces from T1-weighted
images and an additional high-resolution T2-weighted image.
% projection
Results were projected onto the cortical surfaces using
\href{https://surfer.nmr.mgh.harvard.edu}{FreeSurfer's} \citep{dale1999cortical}
'mri\_vol2surf' command.
% smoothing
After projection, individual PPA ROIs were spatially smoothed applying a
Gaussian kernel with full width at half maximum (FWHM) of \unit[2.0]{mm}.

>>>>

\todo[inline]{I added table of contents \& figure. s. Guidelines: ``A table of
contens should be included on the first page, listing the page number of each
supplementary figure``}

\todo[inline]{add the references to mainmanuscript (see ``??'') because
cross-referencing does not work in the pdf that gets compiled first}

@@

% individiaul results; intro
Figure~\ref{fig:subjs_ao_av_c1_surf} shows the individual results of
the movie's primary contrast (\texttt{vse\_new > vpe\_old}) and
audio-description's primary contrast (\texttt{geo, groom} > non-spatial noun
categories) mapped onto subject-specific cortical surfaces.
% reconstruction
% \href{https://github.com/psychoinformatics-de/studyforrest-data-freesurfer.git}{dataset}
\href{https://surfer.nmr.mgh.harvard.edu}{FreeSurfer} v5.3.0
\citep{dale1999cortical} was used to reconstruct surfaces from T1-weighted
images and an additional high-resolution T2-weighted image
\citep{hanke2016freesurferdata}.
% projection
Results were projected onto the cortical surfaces using
\href{https://surfer.nmr.mgh.harvard.edu}{FreeSurfer's} \citep{dale1999cortical}
'mri\_vol2surf' command.
% smoothing
After projection, individual PPA ROIs were spatially smoothed applying a
Gaussian kernel with full width at half maximum (FWHM) of \unit[2.0]{mm}.
